Make any stupid plot you want

### 2020-12-31 draft/sections/abstract.tex
slight rewording

The Python Matplotlib visualization library grew organically such that the visualization functions are deeply entangled with the data the functions expect in such a way that it has become hard to adapt the library for modern needs. To rearchtecture the library while not sacrificing its current very high degree of flexiblity, we developed a model that preserves the structure of the data while also putting very few constraints on the data it can encode.

We propose that afunction that converts data into a graphic is the composition of two functions: a set of equivariant maps from data to visual channels and an equivariant map that assembles the visual channels into a graphic renderable by a physical display. We encode data as a fiber bundle to separately consider the fields of the data (the variables) as the fiber and the connectivity as the base space. We also represent prerender display spaces as a fiber bundle with a base space that is a continous map into the data base space, thereby preserving the connectivity of the data in the graphic.

>>>>

The Python Matplotlib visualization library grew organically such that the visualization functions are deeply entangled with the data the functions expect in such a way that it has become hard to adapt the library for modern needs. To rearchtecture the library while not sacrificing its current very high degree of flexiblity, we developed a model of visualization that preserves the structure of the data while also putting very few constraints on the data it can encode.

We propose that a function that converts data into a graphic is the composition of two functions: a set of equivariant maps from data to visual channels and an equivariant map that assembles the visual channels into a graphic renderable by a physical display. We encode data as a fiber bundle to separately consider the fields of the data (the variables) as the fiber and the connectivity as the base space. We also represent prerender display spaces as a fiber bundle with a base space that is a continous map into the data base space, thereby preserving the connectivity of the data in the graphic.
